IML Term project

### 2022-12-03 main_markdown.rmd

# Poistetaan sarakkeet id, date, class4, partlybad
npf <- npf[, -(1:4)]

@@

>>>>

# Poistetaan sarakkeet id, date, class4, partlybad
npf <- npf[, -(1:4)]
```

@@

```{r glm}
mod1<-glm(class2~., npf, family=binomial(link="logit"))
mod2<-glm(class2~., npf, family=binomial(link="probit"))
plot(mod1)
prob1<-predict(mod1, npf, type="response")
pred1<-c()
perp1<-c()
for(i in 1:dim(npf)[1]){
  if(prob1[i]>=0.5){
    pred1<-c(pred1,1)
  } else{
    pred1<-c(pred1,0)
  }
  if(npf$class2[i]==1){
    perp1<-c(perp1,prob1[i])
  } else{
    perp1<-c(perp1,1-prob1[i])
  }
}
mean(pred1==npf$class2)
exp(-mean(perp1))
```

```{r lassoridge}
mod3<-cv.glmnet(x=as.matrix(npf[,1:100]), y=npf[,101],alpha=1, family="binomial", type.measure="class")
mod4<-cv.glmnet(x=as.matrix(npf[,1:100]), y=npf[,101],alpha=0, family="binomial", type.measure = "class")
mod3a<-glmnet(x=as.matrix(npf[,1:100]), y=npf[,101],alpha=1, family="binomial", lambda=mod3$lambda.min)
coef(mod3)
plot(mod3a)
plot(mod3$glmnet.fit, xvar="lambda")
prob3a<-predict(mod3a, newx=as.matrix(npf[,1:100]), type="response")
pred3a<-c()
perp3a<-c()
for(i in 1:dim(npf)[1]){
  if(prob3a[i]>=0.5){
    pred3a<-c(pred3a,1)
  } else{
    pred3a<-c(pred3a,0)
  }
  if(npf$class2[i]==1){
    perp3a<-c(perp3a,prob3a[i])
  } else{
    perp3a<-c(perp3a,1-prob3a[i])
  }
}
mean(pred3a==npf$class2)
exp(-mean(perp3a))
mod4a<-glmnet(x=as.matrix(npf[,1:100]), y=npf[,101],alpha=0, family="binomial", lambda=mod4$lambda.min)
plot(mod4a)
plot(mod4$glmnet.fit, xvar="lambda")
prob4a<-predict(mod4a, newx=as.matrix(npf[,1:100]), type="response")
pred4a<-c()
perp4a<-c()
for(i in 1:dim(npf)[1]){
  if(prob4a[i]>=0.5){
    pred4a<-c(pred4a,1)
  } else{
    pred4a<-c(pred4a,0)
  }
  if(npf$class2[i]==1){
    perp4a<-c(perp4a,prob4a[i])
  } else{
    perp4a<-c(perp4a,1-prob4a[i])
  }
}
mean(pred4a==npf$class2)
exp(-mean(perp4a))
```
```{r svm}
modsv<-tune(svm, class2~., data=npf, kernel="linear", scale=FALSE, ranges=list(cost=c(0.001, 0.01, 0.1, 1, 2, 5)))
modsvm<-svm(class2~., data=npf, kernel="linear", scale=FALSE, cost=0.001,probability=TRUE)
sv_best<-modsv$best.model
predsv<-predict(modsvm,newdata=npf)
predsv2<-predict(modsvm,newdata=npf,probability = T)
probsv<-attr(predsv2, "probabilities")
perpsv<-c()
for(i in 1:dim(npf)[1]){
  if(npf$class2[i]==0){
    perpsv<-c(perpsv, probsv[i,2])
  } else{
    perpsv<-c(perpsv, probsv[i,1])
  }
  }
mean(predsv==npf$class2)
exp(-mean(log(perpsv)))
```
